{\bf {\Large Title....}}

### 2016-07-08 ident_manu.Rnw
category error ranges added to text

# L1 range within categories
# sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
#   sens_ests_cat[., ] %>% 
#   mutate(
#     error = sapply(error, scinot),
#     Parameter = par_txt(Parameter)
#     )

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).  Within categories, sensitivity ranged from

>>>>

# L1 range within categories
sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
  lapply(., function(x){

    with(x, which(error %in% range(error))) %>% 
      x[., ] %>% 
      mutate(
        Parameter = par_txt(Parameter), 
        error = sapply(error, scinot)
      )

    }
  )

# # average L1 within each category
# sensave <- group_by(sens_ests_cat, Category) %>% 
#   summarize(error = mean(error))

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).  Within categories, sensitivity ranged from \Sexpr{sensrngcat$Optics$error[1]} (\Sexpr{sensrngcat$Optics$Parameter[1]}) to \Sexpr{sensrngcat$Optics$error[2]} (\Sexpr{sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{sensrngcat$`Organic Matter`$error[1]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{sensrngcat$`Organic Matter`$error[2]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{sensrngcat$Phytoplankton$error[1]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{sensrngcat$Phytoplankton$error[2]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) for phytopankton, \Sexpr{sensrngcat$Temperature$error[1]} (\Sexpr{sensrngcat$Temperature$Parameter[1]}) to \Sexpr{sensrngcat$Temperature$error[2]} (\Sexpr{sensrngcat$Temperature$Parameter[2]}) for temperature, and \Sexpr{sensrngcat$Zooplankton$error[1]} (\Sexpr{sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{sensrngcat$Zooplankton$error[2]} (\Sexpr{sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{fig:sensplo}, bottom).  Average sensitivity values in each category were

### 2016-07-08 ident_manu.tex
category error ranges added to text

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Thu Jul 7 15:16:18 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temparature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton).

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Fri Jul 8 16:33:07 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temperature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton).  Within categories, sensitivity ranged from $3.18\times 10^{-6}$ (\textit{Kcdom}) to $1.64$ (\textit{astar490}) for optics, $0.01$ (\textit{KGcdom}) to $2.11$ (\textit{k11}) for organic matter, $1\times 10^{-5}$ (\textit{Ksi$_{p1}$}) to $328.35$ (\textit{Qc$_{p1}$}) for phytopankton, $0.12$ (\textit{Tref(nospA+nospZ)$_{p1}$}) to $2.9$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $0$ (\textit{ZQp$_{z1}$}) to $0.82$ (\textit{ZKa$_{z1}$}) for zooplankton (\cref{fig:sensplo}, bottom).
